Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-09 paper-kelompok/main.tex
Minor change
Add measuring principles

\section{Methods}
\subsection{System Overview}
The proposed system consists of five subsystems which are light source, light sensor, control, user interface, and power subsystem. Its data flow diagram (DFD) is shown in Fig. \ref{system-dfd}. The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector. The source light, which is emitted by a polychromatic light source, will be passed through the sample droplet located on an electrode of a DMF platform. The light which is not absorbed by the droplet will pass through the slit then to a monochromator. The monochromator decomposes the light into monochromatic light to be detected by the photodetector array. Each detector in the array measures the light intensity for a specific wavelength. The measurement readings will be sent to the control subsystem to be computed into absorbance values.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{light-source-dfd.png}}
    \caption{DFD of the light source subsystem}
    \label{light-source-dfd}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.33]{light-sensor-dfd.png}}
    \caption{DFD of the light sensor subsystem}
    \label{light-sensor-dfd}
    \end{figure}

@@

@@

The dimension produced are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
Product dimensions are affected by the number of components used in the system and the optical configuration used. 
The sensor's location, diffraction grating, and light source mainly influence the product's height. 
The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.

@@

\begin{thebibliography}{00}
\bibitem{b1} H. V. Tran et al., “Silver nanoparticles-decorated reduced graphene oxide: A novel peroxidase-like activity nanomaterial for development of a colorimetric glucose biosensor,” Arabian Journal of Chemistry, vol. 13, no. 7, pp. 6084–6091, Jul. 2020, doi: 10.1016/j.arabjc.2020.05.008.
\bibitem{b2} Z. Gu, M. L. Wu, B. Y. Yan, H. F. Wang, and C. Kong, “Integrated Digital Microfluidic Platform for Colorimetric Sensing of Nitrite,” ACS Omega, vol. 5, no. 19, pp. 11196–11201, May 2020, doi: 10.1021/acsomega.0c01274.
\bibitem{b3} S. Huang and R. B. Fair, “Quantitative measurements of inorganic analytes on a digital microfluidics platform,” SN Applied Sciences, vol. 1, no. 12, Dec. 2019, doi: 10.1007/s42452-019-1693-8.
\end{thebibliography}

>>>>

\section{Materials and Methods}
\subsection{System Overview}
The proposed system consists of five subsystems which are light source, light sensor, control, user interface, and power subsystem. Its data flow diagram (DFD) is shown in Fig. \ref{system-dfd}. The light sensor subsystem is composed of a slit, a monochromator, and an array of photodetector. The source light, which is emitted by a polychromatic light source, will be passed through the sample droplet located on an electrode of a DMF platform. The light which is not absorbed by the droplet will pass through the slit then to a monochromator. The monochromator decomposes the light into monochromatic light to be detected by the photodetector array. Each detector in the array measures the light intensity for a specific wavelength. The measurement readings will be sent to the control subsystem to be computed into absorbance values.

@@

@@

@@

The absorbance \emph{A} of a particular sample is computed by the Equation (\ref{absorbance}).

    \begin{equation}
    A=-\log10{T}=\log{\frac{{I_{0}}{I}}}
    \label{absorbance}
    \end{equation}

Transmittance \emph{T} is the percentage of incident radiation that the sample transmits, \emph{I_{0}} denotes the intensity of polychromatic light entering the sample, and \emph{I} denotes the intensity of light leaving the sample;
Absorbance is directly proportional to the path length \emph{l} through the medium and the concentration \emph{c} of the absorbing substance for monochromatic radiation.
Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements (\emph{\epsilon} is the molar attenuation coefficient)\cite{b4}.

    \begin{equation}
    A={\epsilon}{l}{c}
    \label{beer-lambert}
    \end{equation}

Beer-Lambert's law states that the concentration of a dilute solution is directly proportional to its absorbance value.
As a result, in the quantization mode, a linear regression is performed to obtain a slope-intercept form linear equation, as follows.

    \begin{equation}
    A={m}{c}+{b}
    \label{linear-eq}
    \end{equation}

where m is the line's slope (gradient) and b is the constant representing the linear equation's y-intercept.

@@

The dimension produced are 120 mm x 131 x 207 mm, as shown in Fig. \ref{device_dimensions}
Product dimensions are affected by the number of components used in the system and the optical configuration used. 
The sensor's location, diffraction grating, and light source mainly influence the product's height. 
The battery has a size of 70 x 42 x 21 mm, which significantly affects the determination of the minimum area of the product base.
In addition, the button component with a diagonal position uses a large enough area but leaves quite a lot of remaining space.

@@

\begin{thebibliography}{00}
\bibitem{b1} H. V. Tran et al., “Silver nanoparticles-decorated reduced graphene oxide: A novel peroxidase-like activity nanomaterial for development of a colorimetric glucose biosensor,” Arabian Journal of Chemistry, vol. 13, no. 7, pp. 6084–6091, Jul. 2020, doi: 10.1016/j.arabjc.2020.05.008.
\bibitem{b2} Z. Gu, M. L. Wu, B. Y. Yan, H. F. Wang, and C. Kong, “Integrated Digital Microfluidic Platform for Colorimetric Sensing of Nitrite,” ACS Omega, vol. 5, no. 19, pp. 11196–11201, May 2020, doi: 10.1021/acsomega.0c01274.
\bibitem{b3} S. Huang and R. B. Fair, “Quantitative measurements of inorganic analytes on a digital microfluidics platform,” SN Applied Sciences, vol. 1, no. 12, Dec. 2019, doi: 10.1007/s42452-019-1693-8.
\bibitem{b4} D. A. Skoog, F. J. Holler, and S. R. Crouch, Principles of Instrumental Analysis, 7th ed. Cengage Learning, 2016.
\end{thebibliography}
